Prediction of the 2020 Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
..

.....

# Data

@@

As previously mentioned, our data is from two different datasets; the Democracy Fund + UCLA Nationscape Wave 50 dataset, and the 2018 1-year American Community Survey (ACS) dataset. They each contain both qualitative and quantitative data. 
To forecast the results of the presidential election, our model was fitted using the Nationscape survey data. The Democracy Fund + UCLA Nationscape is "one of the largest public opinion surveys ever conducted -- interviewing people in nearly every county, congressional district, and mid-sized U.S. city in the lead up to the 2020 election." @citevavreck_tausanovitch_2020] Consequently, interviewing "roughly 6,250 per week" was part of the survey methodology employed by Nationscape. As such, the Nationscape Wave 50 dataset contains results for 6,479 interviews conducted during the week of June 25-July 1, 2020. It can be accessed by visiting https://www.voterstudygroup.org/publication/nationscape-data-set and submitting a request to access the data [@vavreck_tausanovitch_2020]. By providing your full name and email address, you will then be emailed a link to the page where it can be downloaded.

Nationscape samples are provided by Lucid, a market research platform that uses their software for conducting online surveys. The Nationscape surveys were completed by participants online in English [tausanovitch_vavreck_reny_hayes_rudkin_2019]. The survey data is then weighted using a simple raking technique, where one set of weights is generated for each week's survey, in an attempt to have data that is representative of their target population. The survey data is weighted on many demographic factors such as gender, age, and nativity.

  At first glance of the Wave 50 data, we noted that it contains 265 variables. This is noteworthy because it allows a more complete picture of voter attitude to be derived from the data compared to if there were less variables. Another strength of this dataset is the overall quality of responses from those surveyed. More specifically, the data does not contain any duplicate records, inappropriate entries, or poor entries (e.g. typos, misspellings); hence, making it easier to work with. This high quality of survey responses can be at least partially attributed to the fact that "Nationscape samples are provided by Lucid, a market research platform that runs an online exchange for survey respondents. [@tausanovitch_vavreck_reny_hayes_rudkin_2019]" What is more, the individuals belonging to the sample are required to "complete an attention check before completing the [online] survey [@tausanovitch_vavreck_reny_hayes_rudkin_2019]." With this method of sample selection, along with the precaution taken to ensure their attentiveness, it is unlikely for survey respondents to submit low-quality responses.

  The main weakness of the Nationscape Wave 50 dataset is the likelihood that it includes sampling error and/or coverage error. While the goal of the Nationscape survey is to determine American voter attitudes, making inferences based only on the Wave 50 dataset would result in sample bias. This is because the target population is all American citizens age 18 years and older, whereas the sample frame is Lucid's online exchange for survey respondents, and the sample is a set of 6,479 individuals from said online exchange which match "a set of demographic criteria [@tausanovitch_vavreck_reny_hayes_rudkin_2019]." It is unlikely that a survey sample of 6,479 American citizens during a single week is representative of American voter attitudes as a whole. This may lead one to wonder why Nationscape chose to use the described sampling approach. Apart from the fact that the survey was conducted every week, the reason is trade-offs. For example, although there is potential coverage error in the data--a common result of online surveys--some trade-offs are a lesser rate of non-response, lower cost, convenience and accuracy. Whilst on the topic of non-response, it is worth mentioning that the variable with greatest amount of non-response in the Wave 50 data set is household income at roughly 5.5%. Nonetheless, this is a much smaller percentage of non-response in household income than is typically seen in political surveys, and Nationscape handles it by not weighting income for non-respondents. Similarly, a statement from Nationscape in its "Representativeness Assessment" implies an overall lack of concern for non-response in the data, as "previous evaluations of the samples Lucid provides have found them to be of high quality [@tausanovitch_vavreck_reny_hayes_rudkin_2019]."

@@

Age:  The age of a respondent. Age was originally a nominal value(numerical), but the data was later grouped into categories for our predictive model, and to match the post-stratification data. This allowed for us to look at how age groups might influence the vote. The 2020 election marks the first time that Millennials and Gen Z will have an equal share of the number of eligible voters as Baby Boomers and earlier generations [@agearticle] . Older voters in the past have had higher turn out rates, so looking at how how age categories tend to vote can give insight on how this will play a factor in the future election. We can see in (Figure \@ref(fig:ageind)) that there is a much smaller proportion of younger voters, but this is the age group that seems to have the strongest Democratic support.

@@

# References
ADD FIVE THIRTY EIGHT CITATION

Tausanovitch, Chris and Lynn Vavreck. 2020. Democracy Fund + UCLA Nationscape, October 10-17, 2019 (version 20200814). Retrieved from [URL].

>>>>

There are a vast number of ways in which statistical analysis can be sued to foretell future political future  political appointment. With that being said, however, the statistical methods one chooses to exploit are usually dependent on the data in question. As such, it is important to both understand, and be able to describe the data before considering the optimal approach in working with it. By staying true to this procedure deriving inferences about some given 
# Data

@@

As previously mentioned, our data is from two different datasets; the Democracy Fund + UCLA Nationscape Wave 50 dataset, and the 2018 1-year American Community Survey (ACS) dataset. They each contain both qualitative and quantitative data. 
To forecast the results of the presidential election, our model was fitted using the Nationscape survey data. The Democracy Fund + UCLA Nationscape is "one of the largest public opinion surveys ever conducted -- interviewing people in nearly every county, congressional district, and mid-sized U.S. city in the lead up to the 2020 election (Tausanovitch, 2020)." Consequently, interviewing "roughly 6,250 per week" was part of the survey methodology employed by Nationscape. As such, the Nationscape Wave 50 dataset contains results for 6,479 interviews conducted during the week of June 25-July 1, 2020. It can be accessed by visiting https://www.voterstudygroup.org/publication/nationscape-data-set and submitting a request to access the data (Tausanovitch, 2020). By providing your full name and email address, you will then be emailed a link to the page where it can be downloaded.

Nationscape samples are provided by Lucid, a market research platform that uses their software for conducting online surveys. Nationscape surveys were completed by participants online in English (Tausanovitch, 2020). The survey data is then weighted using a simple raking technique, where one set of weights is generated for each week's survey, in an attempt to have data that is representative of their target population. The survey data is weighted on many demographic factors such as gender, age, and nativity.

  At first glance of the Wave 50 data, we noted that it contains 265 variables. This is noteworthy because it allows a more complete picture of voter attitude to be derived from the data compared to if there were less variables. Another strength of this dataset is the overall quality of responses from those surveyed. More specifically, the data does not contain any duplicate records, inappropriate entries, or poor entries (e.g. typos, misspellings); hence, making it easier to work with. This high quality of survey responses can be at least partially attributed to the fact that "Nationscape samples are provided by Lucid, a market research platform that runs an online exchange for survey respondents(Tausanovitch, 2020)". What is more, the individuals belonging to the sample are required to "complete an attention check before completing the [online] survey (Tausanovitch, 2020)." With this method of sample selection, along with the precaution taken to ensure their attentiveness, it is unlikely for survey respondents to submit low-quality responses.

  The main weakness of the Nationscape Wave 50 dataset is the likelihood that it includes sampling error and/or coverage error. While the goal of the Nationscape survey is to determine American voter attitudes, making inferences based only on the Wave 50 dataset would result in sample bias. This is because the target population is all American citizens age 18 years and older, whereas the sample frame is Lucid's online exchange for survey respondents, and the sample is a set of 6,479 individuals from said online exchange which match "a set of demographic criteria (Tausanovitch, 2020)." It is unlikely that a survey sample of 6,479 American citizens during a single week is representative of American voter attitudes as a whole. This may lead one to wonder why Nationscape chose to use the described sampling approach. Apart from the fact that the survey was conducted every week, the reason is trade-offs. For example, although there is potential coverage error in the data--a common result of online surveys--some trade-offs are a lesser rate of non-response, lower cost, convenience and accuracy. Whilst on the topic of non-response, it is worth mentioning that the variable with greatest amount of non-response in the Wave 50 data set is household income at roughly 5.5%. Nonetheless, this is a much smaller percentage of non-response in household income than is typically seen in political surveys, and Nationscape handles it by not weighting income for non-respondents. Similarly, a statement from Nationscape in its "Representativeness Assessment" implies an overall lack of concern for non-response in the data, as "previous evaluations of the samples Lucid provides have found them to be of high quality (Tausanovitch, 2020)."

@@

Age:  The age of a respondent. Age was originally a nominal value(numerical), but the data was later grouped into categories for our predictive model, and to match the post-stratification data. This allowed for us to look at how age groups might influence the vote. The 2020 election marks the first time that Millennials and Gen Z will have an equal share of the number of eligible voters as Baby Boomers and earlier generations [@agearticle]. Older voters in the past have had higher turn out rates, so looking at how how age categories tend to vote can give insight on how this will play a factor in the future election. We can see in (Figure \@ref(fig:ageind)) that there is a much smaller proportion of younger voters, but this is the age group that seems to have the strongest Democratic support.

@@

# References

Tausanovitch, Chris and Lynn Vavreck. 2020. Democracy Fund + UCLA Nationscape, October 10-17, 2019 (version 20200814). Retrieved from https://www.voterstudygroup.org/publication/nationscape-data-set.
